### 2021-09-15 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
comment on LFR power density/temperature constraint

Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C. 
%\mw{Make sure numbers are in math mode -BW}
The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side. LFR sCO$_2$ inlet low temperature has a lower bound of $340^{\circ}$C and an optimal value of $400^{\circ}$C, as provided by Westinghouse.
%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.

>>>>

Where the left hand side, $\dot{m}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transferred into the cycle, $\dot{Q}_{LFRHX}$, is set at $950$ MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of $595^{\circ}$C. 
%\mw{Make sure numbers are in math mode -BW}
The outlet temperature of the LFR is specified, accounting for the high temperature material limits on the LFR lead side. LFR sCO$_2$ inlet low temperature has a lower bound of $340^{\circ}$C and an optimal value of $400^{\circ}$C, as provided by Westinghouse.
%\mw{How do we know that 400C is the optimal temperature? This information is given to us by Westinghouse, right? -BW} 
\bl{In an LFR, the outlet temperature is limited by materials considerations. The flow velocity is limited by erosion of the fuel (if the lead gets too fast, it erodes the fuel). We want the core to be compact. Therefore the mass flow is limited. This means that a lower inlet temperature gives a higher power (subject to constraints on fuel temperautre, which is also a function of power density). There is a limit of about 340C, below which the lead might freeze (which is operationally unacceptable), but until that value, lower inlet = higher core power. However, from thermodynamics, higher inlet = higher efficiency. There is a trade-off between driving the core harder and getting better cycle performance. The trade-off gives 400C as a temperature that doesnt overly compromise core power while still providing reasonable efficiency. Raising this temperature higher would drop the core power below the 950 MW}
Increasing the sCO$_2$ LFR inlet temperature above this optimal value leads to diminishing returns on the LFR efficiency.
